TBD

### 2016-10-07 paper.tex
need to rewrite stefcal section

On the odd iterations $\lambda$ is chosen to be zero, which corresponds to an $\alpha$ equal to one. On the even iteration $\lambda$ is chosen to be equal to one, which corresponds
to an $\alpha$ equal to a half. On the odd iteration

\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}

Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule .

>>>>

On the odd iterations $\lambda$ is chosen to be zero, which corresponds to an $\alpha$ equal to one. On the even iteration $\lambda$ is chosen to be equal to one, which corresponds
to an $\alpha$ equal to a half. Note that, on the odd iteration the influence that the estimate of the parameters of the previous iteration has on the current estimate is scaled
by a half. Which is exactly the same as in, Eq.~\eqref{eq:one_half}.

If we wish to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two.

At this point there is no way of knowing if this is mere coincidence. DEF REWRITE THIS.

REWRTIE THIS IN A DIFFERENT WAY. START WITH CHENGULAR AND JUST MENTION THE LINK TO STEFCAL'S CHOICE OF ALPHA.

The update rules in Eq.~\eqref{eq:lambda} and Eq.~\eqref{eq:alpha} have been derived before, by Chengular... The approach they followed is discussed in the Appendix.

Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule.

In an attempt to merge the terminology that has independently develop in the general calibration and redundant calibration literature and to emphasize the close
relationship between Stefcal and the approach derived by I will use the label Redunandat SteFCal (R-Stefcal) to refer to the NLS method proposed by ...
